---
title: "Week3Assgntpresentation"
subtitle: "Please click left-right arrow buttons to view presentation"
author: "pduchesne"
date: "3 December 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,warning = FALSE)
```

## Week 3 Assignment

A web page using R Markdown that features a Plotly chart.  

The data for this assignment is sourced from STATEC, the Luxemburgish statistics bureau:
Evolution of total, luxembourgish and foreign population 1961 - 2017 © STATEC / CTIE found at <http://www.statistiques.public.lu/stat/TableViewer/tableView.aspx?ReportId=12858&IF_Language=eng&MainTheme=2&FldrName=1>.

We have downloaded the csv file to load it into a data frame and prepared it to focused our attention on the year 2000 - 2017 data.
```{r load_popLU_data, message=FALSE, warning=FALSE}
#
set.seed=(29092015)
library(dplyr);
#load csv file available at source web site
df_file <- read.csv("./b1115.csv", header = FALSE, sep = ",", quote = "\"",na.strings="", stringsAsFactors=FALSE)
library(reshape)
library(stringr)
#cleanup the data
hdr<-str_trim(df_file[,1],side="both")
df_population <- as.data.frame(t(df_file))
names(df_population)<-c(hdr)
names(df_population)[3]<-"Total_pop"
names(df_population)[6]<-"Prop_Fr"
df_population<-df_population[-c(1),]
df_population$Year<-as.numeric(df_population[,1])
df_population$Total_pop<-as.numeric(df_population[,3])
df_population$Luxembourgers<-as.numeric(df_population[,4])
df_population$Foreigners<-as.numeric(df_population[,5])
#subset the data
df_population2k<-subset(df_population,Year>=2000)

```

## Plotly Chart
We have used Plotly to advantage in order to enhance the Bar Chart by layering in the Proportion of foreigners (in %) as a Line Chart over the Grouped Bar Chart.

```{r pressure, echo=FALSE, message=FALSE, warning=FALSE}
library(plotly)
plot_ly(df_population2k) %>%
        add_trace(x = ~Year, y = ~Luxembourgers, type = 'bar', name = 'Luxembourgers', marker = list(color = '#FFD700', line = list(color = '#FFB90F', width = 1)),
            hoverinfo = "text",
            text = ~Luxembourgers) %>%
         add_trace(x = ~Year, y = ~Foreigners, type = 'bar', name = 'Foreigners',
            marker = list(color = '"#FF3030', line = list(color = '#CD6600', width = 1)),
            hoverinfo = "text",
           text = ~Foreigners) %>%
         add_trace(x = ~Year, y = ~Total_pop, type = 'bar', name = 'Total population',
            marker = list(color = '#6495ED', line = list(color = 'rgb(8,48,107)', width = 1)),
            hoverinfo = "text",
            text = ~Total_pop) %>%
         add_trace(x = ~Year, y = ~Prop_Fr, type = 'scatter', mode = 'lines', name = 'Proportion of foreigners (in %)', yaxis = 'y2',
            line = list(color = '#8B0000'),
            hoverinfo = "text",
            text = ~Prop_Fr) %>%
  layout(title = 'Evolution of total, luxembourgish and foreign population 2000 - 2017',
         xaxis = list(title = "", tickangle = -45),
         yaxis = list(side = 'left', title = 'Population'
#                     , showgrid = FALSE, zeroline = FALSE
                      ),
         yaxis2 = list(side = 'right', overlaying = "y", title = 'Proportion of foreigners (in %)', showgrid = FALSE, zeroline = FALSE),
barmode = 'group', 
bargap = 0.15#, bargroupgap = 0.1
)        
```

© STATEC / CTIE (http://www.statistiques.public.lu/en/support/notice/index.html#copyright)

